---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Lab3package

<!-- badges: start -->
<!-- badges: end -->

The goal of Lab3package is to draw country maps and plotting the lines.

## Installation

You can install the development version of Lab3package like so:

``` r
# install.packages("Lab3package")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(tidyverse)
library(finalproject)
## data
file=dataclean("https://www.ers.usda.gov/webdocs/DataFiles/48747/Unemployment.csv")
str(file)
## plot 

database <- stateunemployed(file,2011,"IA")

database %>%  
  ggplot(aes(x=Area_name,y=Value,fill=county_percent))+geom_col()+
    scale_fill_discrete("Percent of Population")+
    xlab(paste("Top 10 County of Chosen State"))+ylab("Population")

database <- localunemployrate(file,"Texas")
database %>%
  ggplot(aes(year,Value,color=Area_name))+geom_point()  +geom_line()+
  scale_color_discrete("Select state vs US")+
  xlab(paste("year"))+ylab("Unemployment rate")

## Correlation plot
chi_pic[file[,6:7]]

##Unemployment_rate
plotunemployed(file, 2018, "NJ")

```
You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.


In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
