---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}

knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# unemployedR

<!-- badges: start -->
<!-- badges: end -->

The goal of `unemployedR` is to visualize unemployed rate and household income compare with time across United States.

Here are links to our GitHub [repository](https://github.com/zzhou93/unemployedR) where the code for the package is stored and to the package [website](https://zzhou93.github.io/unemployedR) where more information about the package is well shown.

And the shiny app can be found under the`inst/shiny-example` folder or ran the `unemployedR::runExample()`.

## Installation

You can install the development version of `unemployedR` like so:

``` r
# install.packages("unemployedR")
```

## Example

This is a basic example which shows you how to solve a common problem:

`dataclean(url)`

This function is used to clean the data for the future plots.

The example shows the structure of the data file after cleaning.

```{r,warning=FALSE, message=F}

library(unemployedR)

# data cleaning
file=dataclean("https://www.ers.usda.gov/webdocs/DataFiles/48747/Unemployment.csv")

str(file)
```

`plotunemployed(file, yr, State.name)`

This function is used to plot the unemployment rate in county level for a specific state and a year.

The example shows the unemployment rate in county level for NJ in 2018.

```{r ,warning=FALSE, message=F}
plotunemployed(file, 2018, "NJ")
```

`plotmedianhouseholdincome(file, State.name)`

This function is used to plot the 2019 median household income in county level for a specific state.

The example shows 2019 median household income in county level for MS

```{r ,warning=FALSE, message=F}
plotmedianhouseholdincome(file,"MS")
```

`plotunemployed_animation(file, State.name)`

This function is used to provide animation plot of the unemployment rate in county level for a specific state.

The example shows unemployment rate in IA from 2000 to 2020.

```{r ,warning=FALSE, message=F}
plotunemployed_animation(file, "IA")
```

`plotunemployed_time(file, local.name)`

This function is used to plot the unemployment rate along with years.

The example shows unemployment rate in IA along with years.

```{r ,warning=FALSE, message=F}
plotunemployed_time(file, "IA")
```

`stateunemployed(file, yr, State.name`

This function is used to plot top 10 unemployed county histogram in selected state and a year.

The example shows top 10 unemployed counties in IA in 2011 histogram.

```{r,warning=FALSE, message=F}
stateunemployed(file, 2011,"IA")
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.


In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
