---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}

knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# finalproject

<!-- badges: start -->
<!-- badges: end -->

The goal of finalproject is to visualize unemployed rate and household income compare with time across United States.

## Installation

You can install the development version of finalproject like so:

``` r
# install.packages("finalproject")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}

library(finalproject)

## data cleaning
file=dataclean("https://www.ers.usda.gov/webdocs/DataFiles/48747/Unemployment.csv")
str(file)

# plot 



## The unemployment rate in county level for a specific state and a year
plotunemployed(file, 2018, "NJ")



## 2019 median household income in county level for a specific state.
plotmedianhouseholdincome(file,"NJ")

## top 10 unemployed county histogram
stateunemployed(file,2011,"IA")

## The unemployment rate along with years
plotunemployed_time(file,"IA")

```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.


In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
