---
title: "USDA database Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{USDA database Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(unemployedR)
library(tidyverse)
```
In this package, we want to introduce an easy method in visualization the economic data by geographic and time. We will use the USDA published unemployment and household income data as the original data source. Since it contains all the county, state and nation levels data from 2000 to 2022. And when visualization the data by geographic, we will the `usmap::us_map()` for each county's longitude and latitude.

``Data clean`` 
```{r}
file=dataclean("https://www.ers.usda.gov/webdocs/DataFiles/48747/Unemployment.csv")
str(file)
```
In the data clean, we first read the CSV file from the [Unemployment and median household income for the U.S., States, and counties, 2000-20](https://www.ers.usda.gov/webdocs/DataFiles/48747/Unemployment.csv) by using the `read.csv()`.
```{r}
file<-read.csv("https://www.ers.usda.gov/webdocs/DataFiles/48747/Unemployment.csv")
head(file)
str(file)
```
The raw data contains all the economic information in one column `Attribute`, the structure of the `Attribute` is `Category_name_year`.First, since the year is always in form of `20xx`, we can use `dplyr::seperate(...,...,sep = -4)` to separate the `category` and `year`.
```{r}
file<-separate(file,Attribute,c("Attribute","year"),sep = -4)
head(file)
str(file)
```
Then we use the `unique` and `table` to figure out what exactly economic information this data set provide.
```{r}
unique(file$Attribute)
table(file$Attribute)
```
The government does not collect all the attributes annually. Only `Civilian_labor_force`, `Employed`, `Unemployed` and `Unemployment_rate` have been fully collected. And for some year, they didn't collect all counties' data for each category. This may result some problem when we visuliaze the data later.
```{r}
table(file$Attribute,file$year)
```

``Mapping the data``
```{r}
#about two pages?#
## The unemployment rate in county level for a specific state and a year
plotunemployed(file, 2018, "NJ")



## 2019 median household income in county level for a specific state.
plotmedianhouseholdincome(file,"NJ")
```

``Plot and portly``
```{r}
#about one page about plot and 2 pages about the shiny app?#
## top 10 unemployed county histogram
#stateunemployed(file,2011,"IA")

## The unemployment rate along with years
#plotunemployed_time(file,"IA")

```

